Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-10 mtjournal.tex
hacked in a summary paragraph for the FA correlations, and some labels

\begin{itemize}
\item EXPT  using n=1 parse for DPM variants

\begin{verbatim}
   metric      r
  --------   -----
  F[dl;lh]   0.226
  BLEU4      0.218  # +1 smoothing
  F[dlh]     0.185
  TER       -0.173
\end{verbatim}

@@

\item EXPT
  expanding n, gamma=0

@@

\item  EXPT
  setting gamma

@@

@@

\section{Correlations with HTER}
\label{sec:hter1}
  Corpus
    Gale translation corpus 2.5; 3 sites, 2 source languages, 4 genres each

>>>>

\begin{itemize}
\item EXPT  using n=1 parse for DPM variants
\label{tab:facorr:subgraphs}
\begin{verbatim}
   metric      r
  --------   -----
  F[dl;lh]   0.226
  BLEU4      0.218  # +1 smoothing
  F[dlh]     0.185
  TER       -0.173
\end{verbatim}

@@

\item EXPT
  \label{tab:facorr:multiparse}
  expanding n, gamma=0

@@

\item  EXPT
\label{tab:facorr:parseweight}
  setting gamma

@@

\subsection{Summary}

In this section, we have presented experiments exploring a number of
variants of the DPM metric against an average fluency/adequacy judgment. The experiments suggest a
best-case variant, where we set:
\begin{displaymath}
  EDPM = F[1g,2g,dl,lh], n=50, \gamma=0.25
\end{displaymath}
in which we choose a $1g,2g,dl,lh$ sub-graph decomposition based on
the improvements from better sub-graphs
(table~\ref{tab:facorr:subgraphs}), multiple parses ($n=50$) based on
table~\ref{tab:facorr:multiparse}, and $\gamma=0.25$, hinted at by
table~\ref{tab:facorr:parseweight}.  We use these EDPM
parameter-settings in the experiments exploring document-level correlations with HTER
(section~\ref{sec:hter1}).

@@

\section{Per-document correlations with HTER}
\label{sec:hter1}
  Corpus
    Gale translation corpus 2.5; 3 sites, 2 source languages, 4 genres each
